### 2019-10-21 tables/01_predictors.Rmd
suppress pkg loading msgs
towards predictor table cleanup

```{r summary_table, eval=TRUE}
library(kableExtra)
library(dplyr)
library(magrittr)

@@

# setwd("tables")
dt <- readRDS("../data/dt.rds") %>%
  dplyr::select(tp:clay_pct, -matches("zoneid"), -matches("pct"), cdl_vars) %>%
  tidyr::gather(key = "variable") %>%
  group_by(variable) %>%
  mutate(value = as.numeric(value)) %>%
  mutate(q10 = quantile(value, probs = c(0.1), na.rm = TRUE),
         q50 = quantile(value, probs = c(0.5), na.rm = TRUE),
         q90 = quantile(value, probs = c(0.9), na.rm = TRUE), 
         ratio = q90 / q10, 
         n = sum(!is.na(value), na.rm = TRUE)) %>%
  dplyr::distinct(signif(q10, 2), signif(q50, 2), signif(q90, 2), ratio, n) %>%
  dplyr::select(variable, 
         q10 = `signif(q10, 2)`,
         q50 = `signif(q50, 2)`, 
         q90 = `signif(q90, 2)`,
         q10_q90_ratio = ratio,
         n) %>%
  left_join(readRDS("../data/dt_units.rds"), by = "variable") %>%
  dplyr::select(variable, units, everything())

>>>>

```{r summary_table, eval=TRUE}
library(kableExtra)
suppressMessages(library(dplyr))
library(magrittr)

pred_key <- read.csv("../data/predictor_key.csv", 
                     stringsAsFactors = FALSE)

@@

# setwd("tables")
dt <- readRDS("../data/dt.rds") %>%
  dplyr::select(tp:clay_pct, -matches("zoneid"), -matches("pct"), cdl_vars) %>%
  tidyr::gather(key = "variable") %>%
  group_by(variable) %>%
  mutate(value = as.numeric(value)) %>%
  mutate(q10 = quantile(value, probs = c(0.1), na.rm = TRUE),
         q25 = quantile(value, probs = c(0.25), na.rm = TRUE),
         q50 = quantile(value, probs = c(0.5), na.rm = TRUE),
         q75 = quantile(value, probs = c(0.75), na.rm = TRUE),
         q90 = quantile(value, probs = c(0.9), na.rm = TRUE), 
         ratio = q90 / q10, 
         n = sum(!is.na(value), na.rm = TRUE)) %>%
  dplyr::distinct(signif(q10, 2), signif(q25, 2), signif(q50, 2), signif(q75, 2), signif(q90, 2), ratio, n) %>%
  dplyr::select(variable, 
         q10 = `signif(q10, 2)`,
         q25 = `signif(q25, 2)`,
         q50 = `signif(q50, 2)`,
         q75 = `signif(q75, 2)`,
         q90 = `signif(q90, 2)`,
         q10_q90_ratio = ratio,
         n) %>%
  left_join(readRDS("../data/dt_units.rds"), by = "variable") %>%
  dplyr::select(variable, units, everything())

dt <- ungroup(dt)
dt <- left_join(dt, pred_key, by = c("variable" = "var"))
dt <- dplyr::filter(dt, !is.na(pretty))
dt <- mutate(dt, pretty = paste0(pretty, " (", units, ")"), 
             IQR = paste0(q25, " - ", q75))
dt <- dplyr::select(dt, Variable = pretty, 
                    Median = q50, IQR)
